---
title: "chemboxR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{chemboxR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Use the following line to include the chemboxR package in your development:

```{r setup}
library(chemboxR)
```

## Using `get_elements()` 

The `get_elements` function will strip a molecule into its base elements along with the count of each element within the molecule and create a dataframe. In order to do this, call the function and pass the molecule as a string such as:

```{r}
get_elements("C2H4")
```

You can also call multiples of one element such as:

```{r}
get_elements("(C2H4)5")
```

```{r}
get_elements('Al2(SO4)3')
```

```{r}
get_elements('LiH2')
```

## Using `is_valid()`

This function will check if the molecule is chemically viable and will output a Boolean response of `True` or `False`. To use this function, call it and pass a molecule as a string:

```{r}
# Calcium carbonate (a common salt)
is_valid('Al2(SO4)3')
```

```{r}
# Sodium hydroxide (a common base)
is_valid('NaOH')
```

```{r}
# Carbonic acid (a common acid)
is_valid('H2CO3')
```

## Using `get_molec_props()` 

This function will output a dataframe of properties of each element that a molecule contains. To use this function call it and pass a molecule as a string:

```{r}
get_molec_props('NaOH')
```

```{r}
get_molec_props('CaCl3')
```

```{r}
get_molec_props('Al2(SO4)3(C2H4)5')
```

## Using `get_combustion_equation()`

This function will output the molecules that result from the combustion of a specified molecule in a dataframe. To use this function, call it and pass the molecule as a string:

```{r}
get_combustion_equation('C2H4')
```

```{r}
get_combustion_equation('C4H6')
```

```{r}
get_combustion_equation('C5H12')
```
